### 2013-02-15 doc/icml2013/regression.tex
cvec notation

Our analysis is based on the low-rank regression framework of
\citet{Tomioka2011} for tensors, which builds off of
\citet{NegahbanWainwright2009} for matrices.
Define the observation operator $\opX(M_p) : \Re^{d\tp{p}} \to \Re^{n}$
mapping compound parameters $M_p$:
\begin{align}
  \opX(M_p; \sD)_i &\eqdef \frac12 \sum_{(x,y) \in \sD} \innerp{M_p}{x\tp{p}}_i, \quad i  \in [n].
\end{align}

@@

\begin{lemma}[\citet{Tomioka2011}, Theorem 1]
Suppose there exists a restricted strong convexity constant $\kappa(\opX)$ such that
$$\frac{1}{2n} \| \opX( \Delta )\|_2^2 \ge \kappa(\opX) \|\Delta\|^2_F \quad \text{and} \quad
\lambda_n \ge \frac{|\opX^*(\eta_p)|}{n}.$$
Then the error of $\hat M_p$ is bounded as follows:
$\| \hat M_p - M_p^* \|_F \le \frac{\lambda_n \sqrt{k}}{\kappa(\opX)}$.
\end{lemma}

@@

\begin{lemma}[lower bound on restricted strong convexity]
Let $\Sigma_p \eqdef \E[\unfold(x\tp{p})\tp{2}]$.
With high probability at least $1-\delta$,
for some constant $c$,
$$\kappa(\opX) \ge c \sigma_\text{min}^p(\Sigma_p)$$,
where
%$\sigma_\text{min}^p(\Sigma_p) = \min_{M_p \in \sM_p : \|M_p\|_F \le 1} \unfold(M_p)^\top \Sigma_p \unfold(M_p)$.
$\sigma_\text{min}^p(\Sigma_p) = \min_{M_p \in \sM_p : \|M_p\|_F \le 1} \trace(\unfold(M_p)^{\otimes 2} \Sigma_p)$.
\end{lemma}
Note that $\sigma_\text{min}$ 
\begin{proof}
Expanding the definition of the observation operator:
$\frac{1}{2n} \|\opX(\Delta)\|_2^2
= \frac{1}{2n} \sum_{(x,y) \in \sD} \innerp{\Delta}{x\tp{p}}^2$.
Unfolding the tensor and letting $\hat\Sigma_p \eqdef \frac{1}{n} \sum_{(x,y) \in \sD} \unfold(x\tp{p})\tp{2}$,
we have 
$\frac{1}{2n} \|\opX(\Delta)\|_2^2
\ge \frac{1}{2} \trace(\unfold(\Delta)\tp{2} \hat\Sigma_p)
\ge \frac{1}{2} \|\Delta\|_F^2 \sigma_\text{min}^p(\hat\Sigma_p)$.

>>>>

Our analysis is based on the low-rank regression framework of
\citet{Tomioka2011} for tensors, which builds off of
\citet{NegahbanWainwright2009} for matrices.
The main challenge is to control the noise $\eta_p(x)$,
which in addition to containing the usual Gaussian part, is also dependent on
$x$, involves the mixing noise and various cross terms.
We first set up some notation to all three regressions (\refeqn{estimateM1}, \refeqn{estimateM2}, and \refeqn{estimateM3}).
Define the observation operator $\opX(M_p) : \Re^{d\tp{p}} \to \Re^{n}$
mapping compound parameters $M_p$:
\begin{align}
  \opX(M_p; \sD)_i &\eqdef \frac12 \sum_{(x,y) \in \sD} \innerp{M_p}{x\tp{p}}_i, \quad i  \in [n].
\end{align}

@@

\begin{lemma}[\citet{Tomioka2011}, Theorem 1]
Suppose there exists a restricted strong convexity constant $\kappa(\opX)$ such that
$$\frac{1}{2n} \| \opX( \Delta )\|_2^2 \ge \kappa(\opX) \|\Delta\|^2_F \quad \text{and} \quad
\lambda_n \ge \frac{\|\opX^*(\eta_p)\|_2}{n}.$$
Then the error of $\hat M_p$ is bounded as follows:
$\| \hat M_p - M_p^* \|_F \le \frac{\lambda_n \sqrt{k}}{\kappa(\opX)}$.
\end{lemma}

@@

\begin{lemma}[lower bound on restricted strong convexity]
Let $\Sigma_p \eqdef \E[\cvec(x\tp{p})\tp{2}]$.
With high probability at least $1-\delta$,
for some constant $c$,
$$\kappa(\opX) \ge c \sigma_\text{min}^p(\Sigma_p)$$,
where
%$\sigma_\text{min}^p(\Sigma_p) = \min_{M_p \in \sM_p : \|M_p\|_F \le 1} \cvec(M_p)^\top \Sigma_p \cvec(M_p)$.
$\sigma_\text{min}^p(\Sigma_p) = \min_{M_p \in \sM_p : \|M_p\|_F \le 1} \trace(\cvec(M_p)^{\otimes 2} \Sigma_p)$.
\end{lemma}
Note that $\sigma_\text{min}$ 
\begin{proof}
Expanding the definition of the observation operator:
$\frac{1}{2n} \|\opX(\Delta)\|_2^2
= \frac{1}{2n} \sum_{(x,y) \in \sD} \innerp{\Delta}{x\tp{p}}^2$.
Unfolding the tensor and letting $\hat\Sigma_p \eqdef \frac{1}{n} \sum_{(x,y) \in \sD} \cvec(x\tp{p})\tp{2}$,
we have 
$\frac{1}{2n} \|\opX(\Delta)\|_2^2
\ge \frac{1}{2} \trace(\cvec(\Delta)\tp{2} \hat\Sigma_p)
\ge \frac{1}{2} \|\Delta\|_F^2 \sigma_\text{min}^p(\hat\Sigma_p)$.
